### 2020-06-16 Report/aws_325ghz_study.tex
added text for AWS-4X and T_r & some polishing

@@

\subsubsection{Training}
%  
\label{sec:qrnn:training}
\begin{figure}[!ht]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
	\label{fig:quantile_loss}
\end{figure}
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz. A separate QRNN is used for each of the 183\,GHz channels. For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz. We assess the performance of the scheme using both three channel and four channel options of 325\,GHz. Two configurations for three channel option are described in Sec.~\ref{sec:}, and both have been used to train QRNN separately. Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option. Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".

To develop the QRNN based correction scheme, we use the same dataset as in the simple scheme . Out of 125\,000 simulations, 90\% are used to train the model, while the rest 10\% is used to evaluate the model's performance during training. In the training process, noise is added to the input according to Eqn~\ref{eq:noise}, every time the training data is exposed to the model. This ensures that the model is exposed to a new dataset on every iteration. Before training, the input data is normalized with mean and standard deviation.

The structure of the QRNN is defined by various hyper-parameters which are tuned to achieve a high-performing model. These parameters determine the structure of the neural network and how the network is trained. We performed a grid search to determine structural parameters: depth (number of hidden layers) and width (number of neurons). The mean quantile loss is used to compare the performance of different hyper-parameter configurations. Figure~\ref{fig:quantile_loss} shows the mean quantile loss when QRNN is trained for predicting clear-sky values for AWS-34 using four channel option. Increasing both layer width and depth has a positive impact on performance of the network, however for four hidden layers, increasing the layer width leads to only small performance gains. On basis of these results, a neural network with four hidden layer and 128 neurons was chosen for training. For the training, we obtained the best performance when trained with a multiple learning rate schedule. We start the training process with a initial learning rate and after a certain number of epochs, the training is updated with a new initial learning rate. We chose the three training schedules with initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20 epochs. The batch size was set to 256 samples.

The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance. 
%

%
\subsection{Prediction accuracy}
%
\begin{figure}[!p]
	\centering
	\includegraphics[height=60mm]{distribution_predicted_C32}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C33}
	\includegraphics[height=60mm]{distribution_predicted_C34}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C35}
	\includegraphics[height=60mm]{distribution_predicted_C36}
	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.  }
	\label{fig:pdf:qrnn}
\end{figure}
We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset. Noise is added to each simulation to mimic a new measurement dataset.

In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Section~\ref{sec:}. Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz. Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out. Both the three channel and four channel QRNN model are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric. The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}. . The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''. For AWS-34, average deviation in the predictions from all three QRNN models are comparable.  The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.32), however with QRNN the skewness is largely reduced and the symmetry in the distributions is reflected in the low skewness values. Among the three set of predictions, option three-b has the most symmetric error distribution but with a relatively large spread. Predictions from option four have the lowest standard deviation (0.620\,K), which is interestingly smaller than the standard deviation of noise (0.641\,K). Though, all three options of 325\,GHz provide a full coverage to the hydrometer impact in AWS-34, predictions from four channel option are slightly more accurate.

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{Channel_C34.png}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
		simulations before and after correction with QRNNs. Predictions from both three channel and four channel options for 325 GHz are shown. }
	\label{fig:qrnn_C34:deviations}
\end{figure}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
	Dataset  		  &   bias &   std &   skewness & fraction  \\
	&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}}
	\label{tab:qrnn:C34}
\end{table}

@@

\subsection{Uncertainty estimation}
%
Quantile regression can be used to construct a probability distribution of the predictions in comparison to simple regression models, which predict only a point estimate of the target. The outputs from QRNN model are subject to uncertainty which can be modeled by the prediction intervals.

@@

A similar uncertainty quantification for other 183\,GHz channels also gives similar results. Thus, assuming the posterior distribution to be gaussian between $\pm 2 \sigma$, the median is the measure of mean of the gaussian distribution, and the estimated error with respect to the true-value gives the spread of the distribution. 
\begin{figure}[!tb]
	\centering
	\includegraphics[height=80mm]{prediction_uncertainty.png}
	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases. The red line represents the uncertainty if underlying distribution is purely Gaussian with standard deviation 0.62\,K. }
	\label{fig:prediction_uncertainty}
\end{figure}

\subsection{QRNN using AWS-4X}
%
\begin{figure}[!tb]
	\centering
	\includegraphics[height=80mm]{Channel_C32_C4X.png}
	\caption{ }
	\label{fig:qrnn_C32_C4X:deviations}
\end{figure}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise                      & -0.001 & 0.451 &              0.020 &      - \\
		uncorrected                & -1.343 & 5.908 &             -7.484 &      - \\
		corrected (AWS-4X)         &  0.008 & 1.514 &             -4.085 &      3.678 \\
		corrected (four channel)   & -0.011 & 0.878 &             -3.030 &      4.930 \\
		\hline
	\end{tabular}
	\caption{ AWS-32 with AWS-4X}
	\label{tab:qrnn:C32:C4X}
\end{table} 
We also tested the QRNN model to predict cloud-free TBs using AWS-4X. In this case, we trained QRNN with measurements from AWS-32 and AWS-4X, to predict the clear-sky cloud free TBs for AWS-32. The model was trained as described in Section~\ref{sec:qrnn:training}, but the width of the network was chosen to be 256 neurons. Other structural and training parameters remain unchanged.

@@

\section{Sensitivity to different receiver noise temperatures}

%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.451 &              0.020 &      - \\
	uncorrected                & -1.342 & 5.908 &             -7.479 &      - \\
	corrected (three channela) & -0.009 & 0.893 &             -3.092 &      4.990 \\
    corrected (three channelb) &  0.009 & 0.888 &             -3.197 &      4.902 \\	
	corrected (four channel)   &  0.006 & 0.860 &             -2.943 &      4.954 \\
		\hline
	\end{tabular}
	\caption{ AWS-32 , Trec = 1800}
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.452 &              0.015 &      0.000 \\
	uncorrected                & -0.975 & 4.703 &             -8.763 &      0.000 \\
	corrected (three channela) &  0.085 & 0.587 &             -0.640 &      4.209 \\
	corrected (three channelb) &  0.062 & 0.605 &             -0.845 &      4.205 \\
	corrected (four channel)   &  0.048 & 0.606 &             -1.112 &      4.264 \\
		\hline
	\end{tabular}
	\caption{ AWS-33, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      &  0.001 & 0.632 &              0.021 &      0.000 \\
	uncorrected                & -0.676 & 3.686 &            -10.301 &      0.000 \\
	corrected (three channela) &  0.079 & 0.646 &             -0.344 &      2.730 \\
    corrected (three channelb) &  0.090 & 0.639 &             -0.405 &      2.582 \\
	corrected (four channel)   &  0.079 & 0.630 &             -0.399 &      2.981 \\
		\hline
	\end{tabular}
	\caption{ AWS-34, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.001 & 0.629 &              0.007 &      0.000 \\
uncorrected                 & -0.417 & 2.654 &            -12.446 &      0.000 \\
corrected (three channela)  &  0.045 & 0.636 &             -0.188 &      1.431 \\
corrected (three channelb)  &  0.081 & 0.640 &             -0.458 &      1.299 \\
corrected (four channel)    &  0.058 & 0.617 &             -0.007 &      1.801 \\
		\hline
	\end{tabular}
	\caption{ AWS-35, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      &  0.002 & 0.882 &             -0.006 &      0.000 \\
uncorrected                & -0.268 & 2.063 &            -12.003 &      0.000 \\
corrected (three channela) &  0.075 & 0.831 &             -0.130 &      1.283 \\
corrected (three channelb) &  0.105 & 0.807 &             -0.080 &      1.136 \\
corrected (four channel)   &  0.093 & 0.826 &             -0.175 &      1.120 \\
		\hline
	\end{tabular}
	\caption{ AWS-36, Trec = 1800 }
	\label{tab:qrnn:C36}
\end{table}

%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.002 & 0.454 &              0.003 &      0.000 \\
uncorrected                 & -1.343 & 5.907 &             -7.483 &      0.000 \\
corrected (three channela)  & -0.017 & 0.877 &             -3.381 &      4.934 \\
corrected (three channelb)  & -0.015 & 0.882 &             -3.177 &      4.974 \\
corrected (four channel)    &  0.028 & 0.876 &             -3.638 &      4.978 \\
		\hline
	\end{tabular}
	\caption{ AWS-32, Trec = 2400 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise                     & -0.003 & 0.448 &              0.005 &      0.000 \\
uncorrected                & -0.979 & 4.709 &             -8.762 &      0.000 \\
corrected (three channela) &  0.057 & 0.628 &             -0.728 &      4.232 \\
corrected (three channelb) &  0.040 & 0.614 &             -0.786 &      4.205 \\
corrected (four channel)   &  0.043 & 0.614 &             -0.798 &      4.232 \\
		\hline
	\end{tabular}
	\caption{ AWS-33, Trec = 2400  }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise                      & -0.001 & 0.638 &              0.006 &      0.000 \\
uncorrected                 & -0.676 & 3.688 &            -10.299 &      0.000 \\
 corrected (three channela) &  0.069 & 0.655 &             -0.396 &      2.666 \\
corrected (three channelb)  &  0.090 & 0.648 &             -0.310 &      2.594 \\
corrected (four channel)    &  0.059 & 0.643 &             -0.340 &      2.937 \\
		\hline
	\end{tabular}
	\caption{ AWS-34, Trec = 2400 }
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      & -0.004 & 0.633 &              0.021 &      0.000 \\
uncorrected                & -0.420 & 2.654 &            -12.449 &      0.000 \\
corrected (three channela) &  0.034 & 0.646 &             -0.389 &      1.479 \\
corrected (three channelb) &  0.076 & 0.647 &             -0.148 &      1.291 \\
corrected (four channel)   &  0.044 & 0.632 &             -0.188 &      1.809 \\
		\hline
	\end{tabular}
	\caption{ AWS-35, Trec = 2400}
	\label{tab:qrnn:C36}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      &  0.005 & 0.884 &             -0.026 &      0.000 \\
uncorrected                & -0.268 & 2.057 &            -11.977 &      0.000 \\
corrected (three channela) &  0.039 & 0.854 &             -0.131 &      1.283 \\
corrected (three channelb) &  0.090 & 0.839 &             -0.096 &      1.108 \\
corrected (four channel)   &  0.059 & 0.850 &             -0.140 &      1.140 \\
		\hline
	\end{tabular}
	\caption{ AWS-36, Trec = 2400 }
	\label{tab:qrnn:C36}
\end{table}

>>>>

\label{sec:channel:configurations}

@@

\subsubsection{Training}
%  
\label{sec:qrnn:training}
\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{quantile_loss.png}
	\caption{The mean quantile loss with different configurations of layer width and hidden layers ($n_h$).}
	\label{fig:quantile_loss}
\end{figure}
In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz. A separate QRNN is used for each of the 183\,GHz channels. For example, to predict clear-sky TBs from AWS-34, the training data is measurements from all channels of 325\,GHz and measurements from the 183\,GHz to be predicted. We assess the performance of the scheme using both three channel and four channel options of 325\,GHz. Two suggestions for three channel option are described in Sec.~\ref{sec:channel:configurations}, and both have been used to train QRNN separately. Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option. Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".

To develop the QRNN based correction scheme, we use the same dataset as in the simple scheme . Out of 125\,000 simulations, 90\% are used to train the model, while the rest 10\% is used to evaluate the model's performance during training. Presently we train QRNN for only nadir sensor viewing angle and the receiver noise $T_r$ = 1200\,K. In the training process, noise is added to the input according to Eqn~\ref{eq:noise}, every time the training data is exposed to the model. This ensures that the model is exposed to a new dataset on every iteration. Before training, the input data is normalized with mean and standard deviation.

The structure of the QRNN is defined by various hyper-parameters which are tuned to achieve a high-performing model. These parameters determine the structure of the neural network and how the network is trained. We performed a grid search to determine structural parameters: depth (number of hidden layers) and width (number of neurons). The quantile loss on the validation set averaged over all predicted quantiles is used to compare the performance of different hyper-parameter configurations. Figure~\ref{fig:quantile_loss} shows the mean quantile loss when QRNN is trained for predicting clear-sky values for AWS-34 using four channel option. Increasing both layer width and depth has a positive impact on performance of the network, however for four hidden layers, increasing the layer width leads to only small performance gains. On basis of these results, a neural network with four hidden layer and 128 neurons was chosen for training. For the training, we obtained the best performance when trained with a multiple learning rate schedule. We start the training process with a initial learning rate and after a certain number of epochs, the training is updated with a new initial learning rate. We chose the three training schedules with initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20 epochs.

The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance. For QRNN models presented here, we did not optimize the type of activation function and batch size. Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 256 samples for all QRNN models.    
%
\subsection{Prediction accuracy}
%
\begin{figure}[!p]
	\centering
	\includegraphics[height=60mm]{distribution_predicted_C32}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C33}
	\includegraphics[height=60mm]{distribution_predicted_C34}\hspace{5mm}% 
	\includegraphics[height=60mm]{distribution_predicted_C35}
	\includegraphics[height=60mm]{distribution_predicted_C36}
	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.  }
	\label{fig:pdf:qrnn}
\end{figure}
\begin{figure}[!p]
	\centering
	\includegraphics[height=85mm]{Channel_C34.png}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
		simulations before and after correction with QRNNs. Predictions from three channel (three-b) and four channel options for 325 GHz are shown. }
	\label{fig:qrnn_C34:deviations}
\end{figure}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
		uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
		corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
		corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
		corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
		\hline
	\end{tabular}
	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}. The labels "three-a", "three-b" correspond to the old and new suggestions of three channels options of 325\,GHz, and the label "four" represents the four channels option.}
	\label{tab:qrnn:C34}
\end{table}

@@

We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset. Noise is added to each simulation to mimic a new measurement dataset.

In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Section~\ref{sec:simple}. Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz. Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out. Both the three channel and four channel QRNN model are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric. The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}. . The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''. For AWS-34, average deviation in the predictions from all three QRNN models are comparable.  The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.32), however with QRNN the skewness is largely reduced and the symmetry in the distributions is reflected in the low skewness values. Among the three set of predictions, option three-b has the most symmetric error distribution but with a relatively large spread. Predictions from option four have the lowest standard deviation (0.620\,K), which is interestingly smaller than the standard deviation of noise (0.641\,K). Though, all three options of 325\,GHz provide a full coverage to the hydrometer impact in AWS-34, predictions from four channel option are slightly more accurate.

\subsection{Uncertainty estimation}
%
\begin{figure}[!tb]
	\centering
	\includegraphics[height=80mm]{prediction_uncertainty.png}
	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases. The red line represents the uncertainty if underlying distribution is purely Gaussian with standard deviation 0.62\,K. }
	\label{fig:prediction_uncertainty}
\end{figure}

Quantile regression can be used to construct a probability distribution of the predictions in comparison to simple regression models, which predict only a point estimate of the target. The outputs from QRNN model are subject to uncertainty which can be modeled by the prediction intervals.

@@

The figure also shows that the uncertainties for all 1000 random cases are concentrated along a narrow width, thus suggesting that the case to case variability of the uncertainty is low.

A similar uncertainty quantification for other 183\,GHz channels also gives similar results. Thus, assuming the posterior distribution to be gaussian between $\pm 2 \sigma$, the median is the measure of mean of the gaussian distribution, and the estimated error with respect to the true-value gives the spread of the distribution.

\subsection{QRNN using AWS-4X}
%
\begin{figure}[!tb]
	\centering
	\includegraphics[height=80mm]{Channel_C32_C4X.png}
	\caption{ Error distributions for measured and predicted AWS-32, when QRNN  model is trained with measurements from AWS-4X. The results from QRNN model trained with four channel 325\,GHz are also shown for comparison. }
	\label{fig:qrnn_C32_C4X:deviations}
\end{figure}

\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		Noise                      & -0.001 & 0.451 &              0.020 &      - \\
		uncorrected                & -1.343 & 5.908 &             -7.484 &      - \\
		corrected (AWS-4X)         &  0.008 & 1.514 &             -4.085 &      3.678 \\
		corrected (four channel)   & -0.011 & 0.878 &             -3.030 &      4.930 \\
		\hline
	\end{tabular}
	\caption{Statistics for the error distributions of AWS-32 shown in Figure~\ref{fig:qrnn_C32_C4X:deviations}. The QRNN model is trained with measurements from AWS-4X and AWS-32.}
	\label{tab:qrnn:C32:C4X}
\end{table} 
We also tested the QRNN model to predict cloud-free TBs using AWS-4X. In this case, we trained QRNN with measurements from AWS-32 and AWS-4X, to predict the clear-sky cloud free TBs for AWS-32. The model was trained as described in Section~\ref{sec:qrnn:training}, but the width of the network was chosen to be 256 neurons. Other structural and training parameters remain unchanged.

@@

The average deviation of the uncorrected measurements to noise-free clear-sky simulations is -1.343\,K and the standard deviation is 5.908\,K. When trained with AWS-4X, the predictions are not very successful in alleviating the cloud impact. Although, the error standard deviation of the predicted dataset is lower, a large negative skewness (-4.085\,K) indicates significantly high uncorrected cloud impact. On the other hand, QRNN predictions trained with 325\,GHz data are also not completely cloud free, but have a slightly better accuracy. The error standard deviation for the four channel option is 0.878\,K.

Clearly, without additional information, QRNN cannot learn to predict cloud free values for AWS-32.
As already seen in simple correction scheme, AWS-4X is not sufficient enough to characterize the effect of hydrometeors in AWS-32.

\section{Sensitivity to different $T_r$}
%
In the previous section, we presented the results from QRNN trained using the three suggestions of 325\,GHz proposed in section~\ref{sec:channel:configurations}. The receiver noise ($T_r$) was assumed to be 1200\,K for all cases. In this section, we explore the sensitivity of QRNN to increasing noise level. The QRNN training is repeated for all three suggestions of 325\,GHz, but with $T_r$ = 1800\,K and $T_r$ = 2400\,K. QRNN is trained with identical structural and training parameters as described earlier. Tables showing the statistics for error distributions for each channel are provided. Table~\ref{tab:qrnn:C32:Trec:1800} - Table~\ref{tab:qrnn:C36:Trec:1800} show the statistics for AWS-32, AWS-33, AWS-34, AWS-35 and AWS-36 respectively, when $T_r$ = 1800\,K.  Similarly Table~\ref{tab:qrnn:C32:Trec:2400} - Table~\ref{tab:qrnn:C36:Trec:2400} show the statistics when $T_r$ = 2400\,K.

For all channels, increase in the measurement noise increases the standard deviation of the predictions. For example, for AWS-34 (four channel option), the error standard deviation is 0.620\,K, 0.630\,K and 0.643\,K for $T_r$ = 1200\,K, 1800\,K and 2400\,K respectively. It is difficult to gauge the impact of increasing noise through bias and skewness of the error distributions, as the distribution can have a large spread, but still be symmetric with low bias and skewness. It is interesting to note that even for 1800\,K, the error standard deviation for predicted values for channels AWS-34, AWS-35 and AWS-36 is smaller than noise. This is in agreement with the results seen for $T_r$ = 1200\,K. However, for $T_r$ = 2400\,K, only AWS-36 follows the trend.

Overall, the results show that an increase in the measurement noise does not have a huge impact on on QRNN accuracy. For the four channel option, with a 100\% increase in noise, the change in standard deviation is less than 10\%.

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                      & -0.001 & 0.451 &              0.020 &      - \\
	uncorrected                & -1.342 & 5.908 &             -7.479 &      - \\
	corrected (three-a) 	   & -0.009 & 0.893 &             -3.092 &      4.990 \\
    corrected (three-b) 	   &  0.009 & 0.888 &             -3.197 &      4.902 \\	
	corrected (four channel)   &  0.006 & 0.860 &             -2.943 &      4.954 \\
		\hline
	\end{tabular}
	\caption{Error statistics for AWS-32, when the model is trained with $T_r$ = 1800\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34} }
	\label{tab:qrnn:C32:Trec:1800}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                       & -0.001 & 0.452 &              0.015 &      - \\
	uncorrected                 & -0.975 & 4.703 &             -8.763 &      - \\
	corrected (three-a) 		&  0.085 & 0.587 &             -0.640 &      4.209 \\
	corrected (three-b) 		&  0.062 & 0.605 &             -0.845 &      4.205 \\
	corrected (four channel)    &  0.048 & 0.606 &             -1.112 &      4.264 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:1800}, but for AWS-33.}
	\label{tab:qrnn:C33:Trec:1800}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	Noise                       &  0.001 & 0.632 &              0.021 &      - \\
	uncorrected                 & -0.676 & 3.686 &            -10.301 &      - \\
	corrected (three-a) 		&  0.079 & 0.646 &             -0.344 &      2.730 \\
    corrected (three-b) 		&  0.090 & 0.639 &             -0.405 &      2.582 \\
	corrected (four channel)    &  0.079 & 0.630 &             -0.399 &      2.981 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:qrnn:C32:Trec:1800}, but for AWS-34. }
	\label{tab:qrnn:C34:Trec:1800}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.001 & 0.629 &              0.007 &      - \\
uncorrected                 & -0.417 & 2.654 &            -12.446 &      - \\
corrected (three-a)  		&  0.045 & 0.636 &             -0.188 &      1.431 \\
corrected (three-b)  		&  0.081 & 0.640 &             -0.458 &      1.299 \\
corrected (four channel)    &  0.058 & 0.617 &             -0.007 &      1.801 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:qrnn:C32:Trec:1800}, but for AWS-35. }
	\label{tab:qrnn:C35:Trec:1800}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                      &  0.002 & 0.882 &             -0.006 &      - \\
uncorrected                & -0.268 & 2.063 &            -12.003 &      - \\
corrected (three-a)        &  0.075 & 0.831 &             -0.130 &      1.283 \\
corrected (three-b)        &  0.105 & 0.807 &             -0.080 &      1.136 \\
corrected (four channel)   &  0.093 & 0.826 &             -0.175 &      1.120 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:1800}, but for AWS-36.}
	\label{tab:qrnn:C36:Trec:1800}
\end{table}

%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
Noise                       &  0.002 & 0.454 &              0.003 &      - \\
uncorrected                 & -1.343 & 5.907 &             -7.483 &      - \\
corrected (three-a)  		& -0.017 & 0.877 &             -3.381 &      4.934 \\
corrected (three-b)  		& -0.015 & 0.882 &             -3.177 &      4.974 \\
corrected (four channel)    &  0.028 & 0.876 &             -3.638 &      4.978 \\
		\hline
	\end{tabular}
	\caption{ Error statistics for AWS-32, when the model is trained with $T_r$ = 1800\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34}  }
	\label{tab:qrnn:C32:Trec:2400}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise                     & -0.003 & 0.448 &              0.005 &      - \\
uncorrected                & -0.979 & 4.709 &             -8.762 &      - \\
corrected (three-a) &  0.057 & 0.628 &             -0.728 &      4.232 \\
corrected (three-b) &  0.040 & 0.614 &             -0.786 &      4.205 \\
corrected (four channel)   &  0.043 & 0.614 &             -0.798 &      4.232 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:2400}, but for AWS-33.  }
	\label{tab:qrnn:C33:Trec:2400}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
 Noise                      & -0.001 & 0.638 &              0.006 &      - \\
uncorrected                 & -0.676 & 3.688 &            -10.299 &      - \\
 corrected (three-a) &  0.069 & 0.655 &             -0.396 &      2.666 \\
corrected (three-b)  &  0.090 & 0.648 &             -0.310 &      2.594 \\
corrected (four channel)    &  0.059 & 0.643 &             -0.340 &      2.937 \\
		\hline
	\end{tabular}
	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:2400}, but for AWS-34.  }
	\label{tab:qrnn:C34:Trec:2400}
\end{table}
